Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-08 bbbq_article.tex
No need of 'bbbq_1_fast' anymore, use 'bbbq_1_smart'
Show number of binders
15-mers for MHC-II nicely shown
Show IC50 values
Show IC50 values that determine a binder per MHC class

% Percentage of spots and spots that overlap with a TMH
\input{bbbq_1_fast/table_f_tmh.latex}

@@

@@

% Percentage of MHC-I 9-mers overlapping with TMH. Values in brackets
% show the number of binders that have at least one residue overlapping with a
% TMH (first value)as well as the number of binders (second value). Percentile
% used: 0.02
% Label: tab:tmh_binders_mhc1
%\begin{sidewaystable}
%  \centering
%  ... centered table here
%\end{sidewaystable}

\input{bbbq_1_fast/table_tmh_binders_mhc1.latex}

@@

%\begin{sidewaystable}
%  \centering
%  \input{../bbbq_1_smart/table_tmh_binders_mhc2.latex}
%\end{sidewaystable}

@@

Per MHC haplotype, we simulated random peptides and measured the
predicted IC50 using \verb;epitope-prediction; (for MHC-I) 
and netmhc2pan (for MHC-II). 
Here, we show the IC50 value per haplotype that
is used to determine if a peptide binds to the haplotype's MHC.
Included in this figure is the MHCnuggets prediction tool,
by \cite{shao2020high}.

% Less pretty 
% 
% \begin{figure}[!htbp]
%   \includegraphics[width=0.9\textwidth]{ic50s_per_haplotype/ic50s_per_haplotype.png}
%   \caption{
%     IC50 values that define a binder
%   }
%   \label{fig:ic50s_per_haplotype}
% \end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{ic50s_per_haplotype/ic50s_per_haplotype_per_mhc_class.png}
  \caption{
    IC50 values that define a binder
  }
  \label{fig:ic50s_per_haplotype}
\end{figure}

\input{ic50s_per_haplotype/ic50s_per_haplotype_1.latex}

\input{ic50s_per_haplotype/ic50s_per_haplotype_2.latex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Relation between hydrophobicity, TMH and MHC binding}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{figure}[!htbp]
%  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/binds_mhc1_vs_binds_mhc2.png}
%  \caption{
%    \richel{Used randomly simulated peptides, results are real}
%  }
%  \label{fig:binds_mhc1_vs_binds_mhc2}
%\end{figure}

%\begin{figure}[!htbp]
%  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/hydrophobicity_vs_binds_mhc1.png}
%  \caption{
%    \richel{Used randomly simulated peptides, results are real}
%  }
%  \label{fig:hydrophobicity_vs_binds_mhc1}
%\end{figure}

%\begin{figure}[!htbp]
%  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/hydrophobicity_vs_binds_mhc2.png}
%  \caption{
%    \richel{Used randomly simulated peptides, results are real}
%  }
%  \label{fig:hydrophobicity_vs_binds_mhc2}
%\end{figure}

%\begin{figure}[!htbp]
%  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/hydrophobicity_vs_is_tmh.png}
%  \caption{
%    \richel{Used randomly simulated peptides, results are real}
%  }
%  \label{fig:hydrophobicity_vs_is_tmh}
%\end{figure}

%\begin{figure}[!htbp]
%  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/is_tmh_vs_binds_mhc1.png}
%  \caption{
%    \richel{Used randomly simulated peptides, results are real}
%  }
%  \label{fig:is_tmh_vs_binds_mhc1}
%\end{figure}

%\begin{figure}[!htbp]
%  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/is_tmh_vs_binds_mhc2.png}
%  \caption{
%    \richel{Used randomly simulated peptides, results are real}
%  }
%  \label{fig:is_tmh_vs_binds_mhc2}
%\end{figure}

@@

>>>>

% Percentage of spots and spots that overlap with a TMH
\input{../bbbq_1_smart/table_f_tmh_2.latex}

@@

Per target proteome (i.e. human, SARS-CoV-2, Mycobacterium tuberculosis),
we collected all 9-mers (for MHC-I) and 15-mers (for MHC-II),
after removing the selenoproteins and proteins that are shorter
than the epitope length.
From these epitopes, per MHC haplotype,
we predicted the IC50 using \verb;epitope-prediction; (for MHC-I)
and MHCnuggets (for MHC-II). 
Here, we show the IC50 value per haplotype that
is used to determine if a peptide binds to the haplotype's MHC.

% tab:ic50_binders_mhc1
\input{../bbbq_1_smart/table_ic50_binders_mhc1_2.latex}

% tab:ic50_binders_mhc2
\input{../bbbq_1_smart/table_ic50_binders_mhc2_2.latex}

@@

% Label: tab:tmh_binders_mhc1
\input{../bbbq_1_smart/table_tmh_binders_mhc1_2.latex}

@@

% Label: tab:tmh_binders_mhc2
\input{../bbbq_1_smart/table_tmh_binders_mhc2_2.latex}

@@

@@

%
% Notes to self
%

%\begin{sidewaystable}
%  \centering
%  ... centered table here
%\end{sidewaystable}
